---
title: "DCC Reporting Dashboard"
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    theme:
      version: 4
      bootswatch: lumen
      primary: '#00A6D6'
      info: '#0C2340'
      success: '#00B8C8'
      warning: '#FFB81C'
      danger: '#E03C31'
    css: custom.css
    orientation: rows
    social: menu
    source_code: "https://github.com/TU-Delft-DCC/dcc_app"
---


```{r setup, include=FALSE}

# Package names
#packages <- c("flexdashboard", "remotes", "googlesheets4", "plotly", "bslib", "data.table", "shiny", "shinyWidgets", "shinydashboard", "shinyjs", "here", "tidyverse", "highcharter")

library(rsconnect)
library(flexdashboard)
library(remotes)
library(googlesheets4)
library(plotly)
library(bslib)
library(data.table)
library(shiny)
library(shinyWidgets)
library(shinydashboard)
library(shinyjs)
library(here)
library(tidyverse)
library(highcharter)


# Install packages not yet installed
#installed_packages <- packages %in% rownames(installed.packages())
 #if (any(installed_packages == FALSE)) {
  #install.packages(packages[!installed_packages])
#}

# Packages loading
#invisible(lapply(packages, library, character.only = TRUE))

# documentation for flexdashboard options: https://rstudio.github.io/flexdashboard/articles/using.html 

# Get the auxiliary info from the tool_kit file
source(here('plot_kit.R'))

# Set the  gpplot theme 
theme_set(dcc_theme)


```


```{r global, include = FALSE}
# The data is public and does not need authentication
gs4_deauth()

dt <- as.data.table(read_sheet("https://docs.google.com/spreadsheets/d/1pEdWUvcnKMdp0KD5XpEhleFqA7hAbDm6VxagN0yTqMU/edit?usp=sharing"))


# change order of levels to reflect chronological order
dt[,date_approx := factor(date_approx, levels = c("Spring 2021", "Summer 2021", "Fall 2021", "Spring 2022", "Fall 2022") ) ]

```

# Sidebar {.sidebar}

### Projects by the DCC

**This is a reporting dashboard for projects completed by the TU Delft Digital Competence Centre (DCC)**.  

For further information about how the DCC can support your FAIR research data management and software development needs, please visit our website at [dcc.tudelft.nl](dcc.tudelft.nl). Documentation and guidance on computing, data, and software for research at TU Delft are maintained on our [DCC Guides](https://tu-delft-dcc.github.io/welcome.html).

### Search

Select from the options below to filter data by support round, faculty, support type, and support status.

```{r filters}
 pickerInput("date_approx","Select DCC support round:", 
              choices= c("All", levels(dt$date_approx) ),
              selected = "All",
              multiple = F,
              )

 pickerInput("faculty","Select faculty:", 
             choices= c("All", sort(unique(dt$faculty))),
             selected = "All",
             multiple = F,
             )
 
 pickerInput('support_type', 'Select support type', 
             choices = c('All',sort(unique(dt$support_type))),
             selected = "All",
             multiple = F,
            ) 
 
 pickerInput('status', label='Select support status', 
            choices = c('All', sort(unique(dt$status))),
            selected= "All",
            multiple=F,
            )
 
```

***Last modified:** 8 November 2022*

```{r filtered-data}
#  Redefining the dataset based on the inputs

dt_selected<-reactive({
  
  dt_selected <- dt[(date_approx %in% if("All" %in% input$date_approx) unique(dt[,date_approx])
                     else input$date_approx )
                    
                    & (faculty %in% if ("All" %in% input$faculty) unique(dt[,faculty]) 
                       else input$faculty)
                    
                    & (support_type %in% if("All" %in% input$support_type)
                      unique(dt[,support_type])  
                       else input$support_type )
                    
                    & (status %in% if("All" %in% input$status) unique(dt[,status])  
                       else input$status ) 
                    ]
  
  dt_selected[,counter:=1]
  
  dt_selected
  
  })

```


# Hosted by the TU Delft Digital Competence Centre

## Row

### Requests received {.value-box}

```{r vbox-nrows}

flexdashboard::renderValueBox({
  
  requests <- nrow(dt_selected()) %>% prettyNum(big.mark = ",")
  
  flexdashboard::valueBox(
    value = requests,
    icon = "fa-list",
    color = "primary"
    )
  
  })
```

### Projects completed {.value-box}

```{r vbox-completed}
flexdashboard::renderValueBox({
  
  completed <- sum(dt_selected()$status == "Completed")  %>% prettyNum(big.mark = ",")
  
  flexdashboard::valueBox(
    value = completed,
    icon = "fa-thumbs-up",
    color = "success"
  )
  
})
```

### Projects running {.value-box}

```{r vbox-running}
flexdashboard::renderValueBox({
  
  running <- sum(dt_selected()$status == "Running")  %>% prettyNum(big.mark = ",")
  
  flexdashboard::valueBox(
    value = running,
    icon = "fa-spinner",
    color = "info"
  )

  })
```

## Row

### Hours assigned {.value-box}

```{r vbox-hrs}
flexdashboard::renderValueBox({
  
  assigned <- sum(dt_selected()$hours_assigned, na.rm = TRUE)  %>% prettyNum(big.mark = ",")
  
  flexdashboard::valueBox(
    value = assigned,
    icon = "fa-clock",
    color = "danger"
    )

  })
```

### Average hours assigned per project {.value-box}

```{r vbox-team}
flexdashboard::renderValueBox({
  
  team <- mean(dt_selected()$hours_assigned, na.rm = TRUE) %>% 
    round() %>%
    prettyNum(big.mark = ",") 
  
  flexdashboard::valueBox(
    value = team,
    icon = "fa-hourglass",
    color = "warning"
    )

  })
```

### Number of applicants {.value-box}

```{r vbox-applicants}
flexdashboard::renderValueBox({
  
  applicants <- length(unique(dt_selected()[["applicant_id"]])) %>% prettyNum(big.mark = ",")
  
  flexdashboard::valueBox(
    value = applicants,
    icon = "fa-user-plus",
    color = "#E0E0E0"
    )
  })
```

## Row

### Requests per support round 

```{r lollipop-round}
# Useful highcharter reference: https://www.tmbish.me/lab/highcharter-cookbook/

renderHighchart({
  
  if (nrow(dt_selected()) != 0){  
    
    x <- dt_selected()[,.N, by = date_approx][order(date_approx)]
    
    x %>% 
      hchart('lollipop', 
             hcaes(x = date_approx, y =  N ),
             name =  "Number of requests",
             dataLabels = list(enabled = TRUE, 
                               text.shadow = NULL,
                               color = 'white',
                               style = list(textOutline = F, 
                                            fontSize = 14, 
                                            fontWeight = 'normal') )) %>%
      hc_plotOptions(
        lollipop = list(connectorWidth = 2, 
                        marker = list(radius = 25))) %>%
      hc_add_theme(dcc_hc_theme) %>%
      hc_yAxis(title = list(label = "Number of requests" , text = "" )) %>%
      hc_xAxis(title = list(label = "Support round" , text = ""))  
    
    } 
  
})
```



### Applications per Status

```{r item-status}
renderHighchart({
  
  if (nrow(dt_selected()) != 0){
    
    x <- dt_selected()[,.N, by = status]
    x[,`:=`(status = fct_reorder(status, -N),
            PCT = round(N/sum(N) *100) 
            )
      ]
    x <- x[order(-N)] 
    
    x %>% 
      hchart(
        "item",
        hcaes(
          name = status,
          y = N,
          label = status
          #color = main_pal[1:nlevels(status)]#[c(1,3,4,2)]
          ),
        name = "Number of requests",
        showInLegend = TRUE 
        ) %>%
      hc_add_theme(dcc_hc_theme)


    
  }
})

```


### Request types 

```{r bubble-type}
renderHighchart({
  
  if (nrow(dt_selected()) != 0){
    
    x <- dt_selected()[,.(unique_id, software, data, workflow)]
    x <- melt(x, id.vars = c("unique_id"), 
              variable.name = "variable", 
              value.name = "value")
    x <-x[, .(N = sum(!is.na(value)) ), by = variable]
    
    
    x %>%
      hchart(
        "packedbubble",
        hcaes(
          name = variable,
          value = N,
          group = variable
          ),
        value = "Number of requests",
        showInLegend = TRUE) %>%
      hc_add_theme(dcc_hc_theme) %>% 
      hc_plotOptions(
        packedbubble = list(
          maxSize = "100%",
          zMin = 0
          )
        )

    
  }
  
})

```

## Row

### Projects by faculty 

```{r hcbar-faculty}

renderHighchart({
  
  if (nrow(dt_selected()) != 0){
    
    y <- dt_selected()[,.(N_requests = .N, N_hours = sum(hours_assigned, na.rm = T)), by =
                         faculty][order(-N_requests)]
    
    highchart() %>% 
      hc_yAxis_multiples(list(title = list(text = "Requests"), opposite = FALSE),
                         list(showLastLabel = FALSE, opposite = TRUE, 
                              title = list(text = "Hours assigned"))) %>%
      hc_xAxis(categories = y$faculty) %>%
      hc_add_series(data = y$N_requests, type = 'column', name = "Number of requests") %>% 
      hc_add_series(data = y$N_hours, yAxis = 1, type = 'column', 
                    name="Number of hours assigned") %>%
      hc_tooltip(crosshairs = TRUE,shared = TRUE) %>%
      hc_add_theme(dcc_hc_theme)

  }  
})

```





