---
title: "DCC Reporting Dashboard"
output:
  flexdashboard::flex_dashboard:
    theme:
      version: 4
      bootswatch: lux
    css: custom.css
    orientation: rows
    social: menu
    source_code: "https://github.com/TU-Delft-DCC/dcc_app"
runtime: shiny
---


```{r setup, include=FALSE}
# Package names
packages <- c("flexdashboard", "remotes", "googlesheets4", "plotly", "bslib", "data.table", 
              "shiny", "shinyWidgets", "shinydashboard", "shinyjs", "here", "tidyverse", "highcharter"
              )

# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# Packages loading
invisible(lapply(packages, library, character.only = TRUE))

# documentation for flexdashboard options: https://rstudio.github.io/flexdashboard/articles/using.html 

bslib::bs_themer()


# Set the  gpplot theme 

theme_set(theme_minimal() + 
            theme(panel.grid.major.x = element_blank())
          )

TU_colors <- list()
TU_colors$main <- '#00A6D6'
TU_colors$secondary<-c ('#0C2340', '#00B8C8', '#0076C2' )

```


```{r get-data}
# The data is public and does not need authentication
gs4_deauth()

dt <- as.data.table(read_sheet("https://docs.google.com/spreadsheets/d/1pEdWUvcnKMdp0KD5XpEhleFqA7hAbDm6VxagN0yTqMU/edit?usp=sharing"))
```

# Sidebar {.sidebar}

### Projects by the DCC

This is a reporting dashboard for projects completed by the Digital Competence Centre (DCC) at TU Delft. For further information and to find out more about how the DCC can support your FAIR research data and software needs, please visit dcc.tudelft.nl. 

### Search
```{r filters}
# dateRangeInput("daterange", "Select date range:",
 #                 start  =  min(wd_data3_sum$APPROVED_DATE),
 #                 end    =  max(wd_data3_sum$APPROVED_DATE),
 #                 min    =  min(wd_data3_sum$APPROVED_DATE),
 #                 max    =  max(wd_data3_sum$APPROVED_DATE),
 #                 format = "dd M yyyy",
 #                 separator = " - ")

#interesting plugin : selectsize: https://stackoverflow.com/questions/60831030/shiny-reactive-selectinput-in-r

 # selectInput("round", label = "Select DCC support round:",
 #             choices = sort(unique(dt$dcc_support_round )), multiple = T, 
 #             selected = sort(unique(dt$dcc_support_round )) 
 #             )


 pickerInput("dcc_support_round","Select DCC support round:", 
             choices= c("All", sort(unique(dt$dcc_support_round))),
             selected = "All",
             multiple = TRUE,
             )

 pickerInput("faculty","Select faculty:", 
             choices= c("All", sort(unique(dt$faculty))),
             selected = "All",
             multiple = TRUE,
             )
 
 pickerInput('support_type', 'Select support type', 
             choices = c('All',sort(unique(dt$support_type))),
             selected = "All",
             multiple = TRUE,
            ) 
 
 pickerInput('status', label='Select support status', 
            choices = c('All', sort(unique(dt$status))),
            selected= "All",
            multiple=TRUE,
            )
```


```{r filtered-data}
#  Redefining the dataset based on the inputs

# filter_faculty <- (faculty %in% if(input$faculty == 'All') unique(dt[,faculty])  else input$faculty )


dt_selected<-reactive({
  dt_selected <- dt[(dcc_support_round %in% if("All" %in% input$dcc_support_round) unique(dt[,dcc_support_round])  else input$dcc_support_round )
     & (faculty %in% if ("All" %in% input$faculty) unique(dt[,faculty]) else input$faculty)
     & (support_type %in% if("All" %in% input$support_type) unique(dt[,support_type])  else input$support_type )
     & (status %in% if("All" %in% input$status) unique(dt[,status])  else input$status ) 
     ]
  
  dt_selected[,counter:=1]
  
  dt_selected
  
  })

```


# Dashboard

## Row

### Requests processed {.value-box}

```{r vbox-nrows}


flexdashboard::renderValueBox({
  requests <- nrow(dt_selected())
  flexdashboard::valueBox(
    value = requests,
    icon = "fa-list",
    color = "primary"
    )
  })
```

### Projects completed {.value-box}

```{r vbox-completed}
flexdashboard::renderValueBox({
  completed <- sum(dt_selected()$status == "Completed")
  flexdashboard::valueBox(
    value = completed,
    icon = "fa-thumbs-up",
    color = "secondary"
  )
})
```

### Projects running {.value-box}

```{r vbox-running}
flexdashboard::renderValueBox({
  running <- sum(dt_selected()$status == "Running")
  flexdashboard::valueBox(
    value = running,
    icon = "fa-spinner",
    color = "success"
  )
})
```

## Row

### Hours assigned {.value-box}

```{r vbox-hrs}
flexdashboard::renderValueBox({
  assigned <- sum(dt_selected()$hours_assigned, na.rm = TRUE)
  flexdashboard::valueBox(
    value = assigned,
    icon = "fa-clock",
    color = "info"
  )
})
```

### Team members {.value-box}

```{r vbox-team}
flexdashboard::renderValueBox({
  team <- 8 #static number
  flexdashboard::valueBox(
    value = team,
    icon = "fa-user",
    color = "warning"
  )
})
```

### Number of applicants {.value-box}

```{r vbox-applicants}
flexdashboard::renderValueBox({
  applicants <- length(unique(dt_selected()[["applicant_id"]]))
  flexdashboard::valueBox(
    value = applicants,
    icon = "fa-user-plus",
    color = "danger"
  )
})
```

## Row

### Requests per status 

```{r bar-round}

renderPlotly({
  if (nrow(dt_selected()) != 0){
  p <- ggplot(data = dt_selected(), aes(x = as.factor(dcc_support_round))) +
  geom_bar(fill = TU_colors$main )+
    geom_text(stat = "count",
              position = position_stack(vjust = 0.5),
              aes(label = after_stat(count)),
              color = 'white')+
    theme(panel.grid.minor = element_blank(),
          axis.title = element_blank()) 
    
  
  ggplotly(p)
  }
})

```

### Requests per round 

```{r pie-status}

renderHighchart({
  if (nrow(dt_selected()) != 0){
  x <- dt_selected()[,.N, by = status]
  x[,PCT:=round(N/sum(N) *100)] 
  
 
  hc <- x %>%
  hchart("pie", hcaes(x = status, y = PCT)) %>%
  hc_tooltip(crosshairs = TRUE, borderWidth = 5, sort = TRUE, shared = TRUE, table = TRUE,
             pointFormat = paste('<b>: {point.percentage:.1f}%</b>')) %>%
  hc_colors(unlist(TU_colors, use.names = F) )
 
  hc 
 }
})

```

## Row

### Projects by faculty 

```{r bar-faculty}

renderPlotly({
  # Create the data for the plot (wide to long)
  if (nrow(dt_selected()) != 0){
  x <- melt(dt_selected(), id.vars = "faculty",
                measure.vars = c("hours_assigned", "counter"))
  x <- x[, .(value = sum(value, na.rm = T)), by = .(faculty, variable)]

  
  p <- ggplot(data = x, aes(x = reorder(faculty,-value) , y = value, fill = variable)) + 
    geom_col( position = "dodge2") + 
    scale_y_continuous("Hours assgined", sec.axis = sec_axis(trans = ~./100, name = "")) 
  
  ggplotly(p)
  }  
})

```

## Row  {.tabset}

# Project descriptions

